%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.3in,top=0.45in,right=0.3in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Brian Sukhnandan} % Your name
\address{https://bitbucket.org/briansukhnandan/ - briansukhnandan.com/} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{ briansukhnandan@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf CUNY Queens College} \hfill {\em September 2017 - Present}
\\ B.S. Computer Science, Minor in Mathematics \hfill { Flushing, NY }
\\ Activities:  QC Game Development Club - Vice President
\\ Expected Graduation Date: December 2021
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & C\#/C++, Java, Python, HTML/CSS/JavaScript, MATLAB \\
Tools \& Software & Unity2D, Git, Microsoft Office Suite \\
Operating Systems \& Technologies &  GNU/Linux, Windows (7/8/10), MacOSX, Raspberry Pi, Arduino \\
\end{tabular}

\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Raspberry Pi 3 Web server}
\\A personal home server which is responsible for hosting several services (such as sites/bots). Also contains several bash scripts to automate command chains such as iptables configurations and scheduled updates, as well as providing shortcuts to improve the overall workflow experience when working strictly through SSH.


{\bf MakerHack 2019@NYU - Dumbo Renovation}
\\Collaborated with teammates to to create a physical map of Dumbo, Brooklyn using LEDs and the Arduino to power different sections of the map based on different conditions. 

{\bf DIY Game Night: Arduino Simon Says}
\\Created a fully functional game of Simon Says on an Arduino! The project features the flashing of LEDs in a random sequence, a passive buzzer followed by a 220-ohm resistor to simulate 8-bit sounds, and a joystick to simulate the flashing of the lights.

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{NASA: Minority University Research \& Education Project}{June 2019 - Present}{Robotics Instructor}{CUNY York College}
\item Created goal-oriented lesson plans to teach basic Electrical Engineering concepts to students through MakeBlock Bot construction and circuit building.
\item Introduced students to basic Computer Science fundamentals through use of the Arduino and open-source text games in Python/C++.
\end{rSubsection}

\begin{rSubsection}{QC Game Development Club}{February 2019 - June 2019}{Project Leader}{CUNY Queens College}
\item Led a team of 2 to design a functioning game using the Unity Engine.
\item Created script outlines in C\# to make implementing new game logic easier.
\end{rSubsection}

\begin{rSubsection}{MinKwon Center for Community Action}{July 2016 - May 2017}{Student Volunteer}{Flushing, NY}
\item Participated in canvassing events such as phone-banking and door-knocking during: \newline
- The NY State Senate Election (August 2016) \newline
- The 2016 General Election
\end{rSubsection}


\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------






\end{document}
